---
title: "quarto-03"
format: docx
editor: visual
---

```{r}
library(reticulate)
use_condaenv("sklearn")
```

------------------------------------------------------------------------

## Table

Markdown table

| Default | Left | Right | Center |
|---------|:-----|------:|:------:|
| 12      | 12   |    12 |   12   |
| 123     | 123  |   123 |  123   |
| 1       | 1    |     1 |   1    |

: Demonstration of pipe table syntax

| fruit  | price |
|--------|------:|
| apple  |  2.05 |
| pear   |  1.37 |
| orange |  3.09 |

------------------------------------------------------------------------

| fruit  | price |
|--------|-------|
| apple  | 2.05  |
| pear   | 1.37  |
| orange | 3.09  |

: {tbl-colwidths="\[75,25\]"}

| Col1 | Col2 | Col3 |
|------|------|------|
| A    | B    | C    |
| E    | F    | G    |
| A    | G    | G    |

: My Caption {#tbl-letters}

See @tbl-letters.

::: {#tbl-panel layout-ncol="2"}
| Col1 | Col2 | Col3 |
|------|------|------|
| A    | B    | C    |
| E    | F    | G    |
| A    | G    | G    |

: First Table {#tbl-first}

| Col1 | Col2 | Col3 |
|------|------|------|
| A    | B    | C    |
| E    | F    | G    |
| A    | G    | G    |

: Second Table {#tbl-second}

Main Caption
:::

See @tbl-panel for details, especially @tbl-second.

```{python}
#| label: tbl-planet-measures
#| tbl-cap: Planets

from IPython.display import Markdown
from tabulate import tabulate
table = [["Sun",696000,1989100000],
         ["Earth",6371,5973.6],
         ["Moon",1737,73.5],
         ["Mars",3390,641.85]]
Markdown(tabulate(
  table, 
  headers=["Planet","R (km)", "mass (x 10^29 kg)"]
))
```

```{r}
#| label: tbl-cars
#| tbl-cap: "Cars"
#| tbl-colwidths: [60,40]

library(knitr)
kable(head(cars))
```

```{r}
#| label: tbl-example
#| tbl-cap: "Example"
#| tbl-subcap: 
#|   - "Cars"
#|   - "Pressure"
#| layout-ncol: 2
#| echo: fenced

library(knitr)
kable(head(cars))
kable(head(pressure))
```

+------------+------------+----------------------+
| Fruit      | Price      | Advantages           |
+============+============+======================+
| Bananas    | \$1.34     | -   built-in wrapper |
|            |            | -   bright color     |
+------------+------------+----------------------+
| Oranges    | \$2.10     | -   cures scurvy     |
|            |            | -   tasty            |
+------------+------------+----------------------+

: Sample grid table.

## Diagram

```{mermaid}
flowchart LR
  A[Hard edge] --> B(Round edge)
  B --> C{Decision}
  C --> D[Result one]
  C --> E[Result two]
```

```{mermaid}
sequenceDiagram
  participant Alice
  participant Bob
  Alice->>John: Hello John, how are you?
  loop Healthcheck
    John->>John: Fight against hypochondria
  end
  Note right of John: Rational thoughts <br/>prevail!
  John-->>Alice: Great!
  John->>Bob: How about you?
  Bob-->>John: Jolly good!
```

```{dot}
//| label: fig-simple
//| fig-cap: This is a simple graphviz graph.
graph G {
  layout=neato
  run -- intr;
  intr -- runbl;
  runbl -- run;
  run -- kernel;
  kernel -- zombie;
  kernel -- sleep;
  kernel -- runmem;
  sleep -- swap;
  swap -- runswap;
  runswap -- new;
  runswap -- runmem;
  new -- runmem;
  sleep -- runmem;
}
```

{{< video local-video.mp4 >}} {{< video https://videos.example.com/video.mp4 >}}

::: callout-note
Note that there are five types of callouts, including: `note`, `warning`, `important`, `tip`, and `caution`.
:::

::: callout-tip
## Tip With Caption

This is an example of a callout with a caption.
:::

::: {.callout-caution collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::

::: {.callout-note icon="false"}
## Pay Attention

Using callouts is an effective way to highlight content that your reader give special consideration or attention.
:::
